---
title: "Lab7"
author: "Asfadhia Zulkifly"
date: "5/12/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Lab 7 WIE180007 R Markdown


1. See basic descriptive

```{r attitude}
library(datasets)
summary(attitude)
```

 * a)	What is the difference between (attitude[4]) and (attitude$learning)

     * attitude$learning
          * returns all of the values in the column labeled learning. 

     * attitude[4]
          * return all values in column index position ‘4’

```{r}
attitude[4]
(attitude$learning)
```

2. Lists name of variables in dataset

```{r}
ls(attitude)
```


3. Calculate number of row in dataset

```{r}
nrow(attitude)
```

4. Calculate number of columns in a dataset

```{r}
ncol(attitude)
```

5.	List structure of a dataset

```{r}
str(attitude)
```

6. See first 6 rows (by default) of dataset

```{r}
head(attitude)
```

7.	See first n rows of dataset
      * Select to see the first 15 rows of dataset
```{r}
head(attitude, n=15)
```

8. See all rows but not the last row

```{r}
head(attitude, n=-1)
```

9.	See last 6 rows (by default) of dataset

```{r}
tail(attitude)
```

10.	See last n rows of dataset
      * Select to see the last 12 rows of dataset.

```{r}
tail(attitude, n=12)
```

11.	See the last n rows but not the first row

```{r}
tail(attitude, -1)
```

12.	Number of missing values
      * Which function will returns number of missing values in each variable of a dataset?

```{r}
sapply(attitude, function(attitude) sum(is.na(attitude)))
```

13.	Number of missing values in a single variable

```{r}
length(attitude[is.na(attitude)])
```

14.	Plot a simple graph, which will appear on a screen device.

```{r}
plot(attitude) 
```

15.	Plot the graph shown below, and make it appear on a file device (a pdf file)

```{r}
pdf(file="lab7plot.pdf")
with(attitude, plot(privileges, learning, main="Learning Attitude"))
```


